Globally-centered autocovariances in MCMC

### 2020-08-06 Paper/main.tex
VAR-1 done dona done done done daara

A critical use of autocovariances is in the assessment of Monte Carlo variability of estimators.  Let $g:\X \longrightarrow \mathbb{R}^d$ be an $F$-integrable function so that we are interested in estimating
%
\[
\mu_g = \mathbb{E}_F[g(X)] = \int_{\X}g(x)F(dx)\;.
\]

Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$ and set $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$.

To assess the reliability of simulations, we are interested in Monte Carlo error, i.e. $\bar{Y_s} - \mu$ for the $s^{th}$ chain. The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
%
{\color{blue} }
\[
\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
\]

>>>>

A critical use of autocovariances is in the assessment of Monte Carlo variability of estimators.  Let $g:\X \longrightarrow \mathbb{R}^p$ be an $F$-integrable function so that interest is in estimating
%
\[
\mu_g = \mathbb{E}_F[g(X)] = \int_{\X}g(x)F(dx)\;.
\]

Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$ and set $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$. By Birkhoff's ergodic theorem,  $\bar{\bar{Y}} \to \mu_g$ as $n \to \infty$ with probability 1.

Reliability of $\bar{\bar{Y}}$ is assessed by its Monte Carlo variability via an asymptotic sampling distribution \citep{fleg:hara:jone:2008,roy:2019,vats:rob:fle:jon:2020}. 
% To assess the reliability of simulations, we are interested in Monte Carlo error, i.e. $\bar{Y_s} - \mu$ for the $s^{th}$ chain. 
% The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov})
 A Markov chain central limit theorem (CLT) holds if there exists a $p \times p$ positive-definite matrix $\Sigma$ such that
%
\begin{equation}
\label{eq:CLT}
  \sqrt{mn}(\bar{\bar{Y}} - \mu) \xrightarrow{d} N(0,\Sigma)\,
\end{equation}
where
\begin{equation}
\label{eq:sigma}
  \Sigma = \sum_{k = -\infty}^{\infty} \Cov_F \left( Y_{11}, Y_{1(1+k)} \right)
\end{equation}
%
The goal in output analysis for MCMC is to estimate $\Sigma$in order to assess variability in $\bar{\bar{Y}}$. There is a rich literature of estimators of $\Sigma$ available for single-chain MCMC implementations. The most common are spectral variance estimators (SVE) \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \cite{chen:seila:1987,vats:fleg:jon:2019}. Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from multiple parallel chains. Batch means estimators are computationally more efficient than SVE, SVE estimators are more reliable \citep{fleg:jone:2010}. Here, we utilize G-ACvF estimators to construct globally-centered SV estimator (G-SVE) of $\Sigma$. Using the methods of \cite{heberle2017fast}, we also provide an efficient algorithm for obtaining the G-SV estimator.
